\documentclass[11pt]{resume}

\usepackage{ebgaramond}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{softblue}{rgb}{0.2,0.4,0.8} % defining custom color

\hypersetup{
    colorlinks=true,
    linkcolor=softblue,      % color of internal links (change box color with linkbordercolor)
    citecolor=softblue,      % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=softblue        % color of external URLs
}

\name{Will Alger}
\address{(502)~$\cdot$~758~$\cdot$~4615 \hfill algerw@icloud.com \hfill \href{https://github.com/Will-Alger}{github.com/will-alger} \hfill \href{https://www.linkedin.com/in/will-alger/}{linkedin.com/in/will-alger}}
\begin{document}


{\centering 
Adaptable CS undergraduate graduating in December 2023 with full-stack experience seeking full-time opportunity. Committed to continuous learning and growth in a dynamic and problem-solving environment.
\par
}
\vspace{10pt}

{\textbf{SKILLS:}} C++, Java, Python, PHP, Typescript, React, jQuery, HTML, CSS, PHPunit, Pyunit, Docker, Git \\
\vspace*{-10pt}

\begin{rSection}{Education}
    \textbf{Northern Kentucky University} \hfill \textit{December 2023} \\ 
    Bachelor of Science, Computer Science \\
    Minor: Foundations of Knowledge Honors: Natural World Cohort \\
    Honors Student \\
    Overall GPA: 3.97/4

\end{rSection}

\begin{rSection}{Experience}

	\begin{rSubsection}{Kroger Technology}{May 2023 - Current}{Software Engineering Intern | Back-end Engineer}{Cincinnati, OH}
        \item Developing Node.js applications in the Customer Identity, Security, and authentication space. 
        \item Improving and maintaining internal microservices and APIs.
        \item Implementing Azure AD B2C Custom policies for customer Sign-in and Sign-up flow.
        \item Supporting migration of legacy systems to Azure Platform.
	\end{rSubsection}
    \vspace*{-5pt}
    \noindent\textbf{Skills:} JavaScript, Node.js, Azure AD B2C, XML, JSON, SDLC, Harness, Azure.
    
    \begin{rSubsection}{}{May 2022 - August 2022}{Software Engineering Intern | Front-end Engineer}{Cincinnati, OH}
        \item Developed and improved internal tools and technology, including dashboards and widgets.
        \item Worked with continuous integration and deployment (CI/CD) pipelines.
        \item Gathered requirements to establish acceptance criteria.
        \item Managed JIRA workflows and collaborated with PMs and designers in cross-functional settings.
    \end{rSubsection}
    \vspace*{-5pt}
    \noindent\textbf{Skills:} TypeScript, React/Reduct, SDLC.

    \vspace*{5pt}
    \begin{rSubsection}{Northern Kentucky University}{Aug 2022 – Dec 2022}{Undergraduate Teaching Assistant}{Highland Heights, KY}
        \item Supported 30+ students in an upper-level computer science course in C++.
        \item Developed and led interactive class workshops and live coding sessions.
        \item Presented a lecture on design patterns.
    \end{rSubsection}
    
    \begin{rSubsection}{Cincinnati Insurance Companies}{Sep 2021 – Nov 2021}{IT Testing Intern}{Cincinnati, OH}
        \item Contributed to functional testing and quality assurance for enterprise insurance policy writing software, adding to the enhancement of system reliability and user experience.
        \item Documented and reported test results and defects meticulously, providing clear and detailed analysis to assist in the identification and resolution of system issues.
    \end{rSubsection}
    \vspace*{-5pt}
    \noindent\textbf{Skills:} Software Testing, Quality Assurance, Defect Documentation, Functional Testing, User Experience Analysis.
\end{rSection}

\begin{rSection}{Projects}

   \begin{rSubsection}{RateMyProfessor Web Scraper -- \href{https://github.com/Will-Alger/rmp-py}{GitHub}}{Ongoing}{}{}
       \item Developing a wrapper to interact with RateMyProfessor’s back-end GraphQL API for an undergraduate research project, allowing data collection of universities, professors, and reviews.
   \end{rSubsection}
   
   
   \begin{rSubsection}{Search Engine for Full-Stack Wiki Application -- \href{https://github.com/Will-Alger/Riki}{GitHub}}{May 2023}{}{}
       \item Implemented an inverted-index based search engine for a full-stack wiki app utilizing Python, Flask, and SQLite with real-time indexing to ensure up to date search results.
       \item Utilized automated unit testing in PyUnit to ensure high-quality code contributions.
       \item Developed comprehensive documentation incorporating requirements traceability, test plan creation, and defect tracking.
   \end{rSubsection}
	
    \begin{rSubsection}{Linear Feedback Shift Register: Visual Tool -- \href{https://will-alger.github.io/LFSR/}{GitHub}}{Nov 2022}{}{}
            \item Developed a dynamic LFSR visualizer on GitHub Pages using JavaScript, jQuery, Bootstrap, HTML \& CSS.
            \item Empowers cryptology students to deepen understanding of digital encryption.
            \item Visualizes a core concept in action for better learning experience.
    \end{rSubsection}
	
\end{rSection}

\begin{rSection}{Campus Involvement}
    \item Sigma Phi Epsilon Fraternity.
    \item Internet of Things (IOT) Club -- Build and develop innovative solutions on the Arduino platform with ESP32 microcontrollers.
    \item Hiking Club.
\end{rSection}

\end{document}